Andres Karjus

### 2019-04-12 index.Rmd
news

- Will be teaching an aRt of the Figure series workshop for the Corpus Linguistics in Scotland network this Friday (12.04), titled [Data visualization with R for corpus linguists](https://andreskarjus.github.io/artofthefigure) (if you registred but haven't received the email for some reason, please get in touch!).

>>>>

- Taught an aRt of the Figure series workshop for the Corpus Linguistics in Scotland network (12.04), titled [Data visualization with R for corpus linguists](https://andreskarjus.github.io/artofthefigure)

- Edinburgh Language Lunch 11.04: (re-)presented the "Modelling lexical interactions in diachronic corpora" poster, originally presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an [online version with interactive plots](https://andreskarjus.github.io/isle_poster) and an (updated!) appendix.
